### 2021-04-08 papers/SYRCoSE/regmachine.tex
Regmachine: small fixes

For our case study we use a simple idealised model 
of a register machine, which consists of a finite 
sequence of instructions, an instruction pointer 
and an infinite set of registers. 
The syntax of the machine's language is 
shown on~\cref{fig:regmachine-syntax}.

@@

We first present the semantics of a single thread program.
In this semantics memory access instructions 
does not actually operate on shared memory,
but rather produce a \emph{label}
denoting the side-effect of the operation 
(see \cref{fig:label-syntax}).
This encoding allows us to decouple 
the semantics of the register machine 
from a \emph{memory model}.

@@

The semantics is given in a form of 
\emph{labelled transition system}~%
\footnote{As we have mentioned, in our \coq development we actually use 
the monadic encoding of the operational semantics. 
The labelled transition system can be deduced from this encoding.}
State of the system consists of instruction pointer
and a map from registers to their values, 
as shown in \cref{fig:regmachine-thrdstate}. 
The rules of the semantics are standard 
(see \cref{fig:regmachine-thrdsem}).

>>>>

For our case study we use a simple idealised model 
of a register machine, which consists of a finite 
sequence of instructions, an instruction pointer 
and an infinite set of registers. 
The syntax of the machine's language is 
shown in~\cref{fig:regmachine-syntax}.

@@

We first present the semantics of a single thread program.
Under this semantics, memory access instructions 
do not operate on shared memory
but rather produce a \emph{label}
denoting the side-effect of the operation 
(see \cref{fig:label-syntax}).
This encoding allows us to decouple 
the semantics of the register machine 
from a \emph{memory model}.

@@

The semantics is given in the form of a
\emph{labelled transition system}~%
\footnote{As we have mentioned, in our \coq development we actually use 
the monadic encoding of the operational semantics. 
The labelled transition system can be derived from this encoding.}
State of the system consists of instruction pointer
and a map from registers to their values, 
as shown in \cref{fig:regmachine-thrdstate}. 
The rules of the semantics are standard 
(see \cref{fig:regmachine-thrdsem}).
